\ttitle

### 2013-10-07 Chapters/Chapter3/one_class_svm.tex

%--------------------------------------------
\subsection{Support Vector Machine}\label{subsec:svm}
We will first discuss the traditional two-class \gls{svm} before we consider the one-class variant, as introduced by Cortes and Vapnik in \cite{cortes1995support}.
Consider a data set $\Omega = \{ (x_1, y_1),\allowbreak (x_2, y_2), \dots , (x_n, y_n) \}$; points $x_i \in \mathbb{R}^d$ in a (for instance two-dimensional) space where $x_i$ is the $\mathcal{I}$-th input data point and $y_i \in \{-1, 1\}$ is the $\mathcal{I}$-th output pattern, indicating the class membership.

@@

This minimization problem can be solved (using \gls{qp}) and transformed to its Lagrange dual formulation.
To do so, the Lagrange multipliers $a_i >= 0$ are introduced and the decision function becomes:
\begin{equation}\label{eq:svm_lagrange}
  f(x) = \operatorname{sgn}( \sum_{i=1}^n \alpha_i y_i K(x, x_i) + b),
\end{equation}
where $K(x, x_i) = \phi(x)^T\phi(x_i)$ (which is further discussed in section \ref{subsec:kernel_trick}).
Here every data point $\mathcal{I}$ for which $a_i > 0$ is weighted in the decision function and thus ``supports'' the classification machine: hence the name ``\acrlong{svm}''.
Since it is shown that under certain circumstances \gls{svm}s show an equality to sparse representations \cite{girosi1998equivalence}, there will often be relatively few Lagrange multipliers with a non-zero value.

@@

The kernel function $K$ can have different forms, such as linear, polynomial and sigmoidal but the most used (and flexible) form is the Gaussian \gls{rbf}, in which the feature space $\mathcal{F}$ is a Hilbert Space of infinite dimensions *** ref needed ***:
\begin{equation}
  K(x, x') = \operatorname{exp} \left( - \frac{ \lVert x - x' \rVert ^2}{2 \sigma^2 } \right),
\end{equation}
where $\sigma \in R$ is a kernel parameter and $\lVert x - x' \rVert$ is the dissimilarity measure expressed in Euclidean distance.

@@

>>>>

%--------------------------------------------
\subsection{Support Vector Machine}\label{subsec:svm}
We will first discuss the traditional two-class \gls{svm} before we consider the one-class variant, as introduced by Cortes and Vapnik in \cite{cortes1995support}.
Consider a data set $\Omega = \{ (x_1, y_1),\allowbreak (x_2, y_2), \dots , (x_n, y_n) \}$; points $x_i \in \mathbb{R}^d$ in a (for instance two-dimensional) space where $x_i$ is the $i$-th input data point and $y_i \in \{-1, 1\}$ is the $i$-th output pattern, indicating the class membership.

@@

This minimization problem can be solved (using \gls{qp}) and transformed to its Lagrange dual formulation.
To do so, the Lagrange multipliers $a_i >= 0$ are introduced and the decision function becomes:
\begin{equation}\label{eq:svm_lagrange}
  f(x) = \operatorname{sgn}( \sum_{i=1}^n \alpha_i y_i K(x, x_i) + b),
\end{equation}
where $K(x, x_i) = \phi(x)^T\phi(x_i)$ (which is further discussed in section \ref{subsec:kernel_trick}).
Here every data point $\mathcal{I}$ for which $a_i > 0$ is weighted in the decision function and thus ``supports'' the classification machine: hence the name ``\acrlong{svm}''.
Since it is shown that under certain circumstances \gls{svm}s show an equality to sparse representations \cite{girosi1998equivalence,smola1998connection}, there will often be relatively few Lagrange multipliers with a non-zero value.

@@

The kernel function $K$ can have different forms, such as linear, polynomial and sigmoidal but the most used (and flexible) form is the Gaussian \gls{rbf}.
As Smola \etal \cite{smola1998connection} state, this Gaussian kernel yields good performance, especially when no assumptions can be made about the data.
The kernel maps input space $\mathcal{I}$ to the feature space $\mathcal{F}$ which is a Hilbert Space of infinite dimensions *** ref needed ***:
\begin{equation}
  K(x, x') = \operatorname{exp} \left( - \frac{ \lVert x - x' \rVert ^2}{2 \sigma^2 } \right),
\end{equation}
where $\sigma \in R$ is a kernel parameter and $\lVert x - x' \rVert$ is the dissimilarity measure expressed in Euclidean distance.

@@

$k(\mathbf{x}_i, \mathbf{x})$ is a kernel function computing a dot product in feature space, introduced by Aizerman \etal \cite{aizerman1964theoretical}.
``Training a \gls{svm} with Gaussian \gls{rbf} kernels corresponds to minimizing the specific cost function with a regularization operator'' \cite{smola1998connection}. \\
``Gaussian kernels tend to yield good performance under general smoothness assumptions and should be considered especially of no additional knowledge of the data is available.'' \cite{smola1998connection}. \\
``Choosing a small width of the kernels leads to high generalization error as it effectively decouples the separate basis functions of the kernel expansion into very localized functions which is equivalent to memorizing the data, whereas a wide kernel tends to oversmooth.'' \cite{smola1998connection}. \\

sparsity, RKHS: \cite{girosi1998equivalence}
